Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble

### 2022-08-30 paper/paper.Rmd
spell check

We conclude that our simplified forecast model may have captured some of the dynamics of the hub ensemble but that more work needs to be done to understand the epidemiological model that represents its behaviour and whether or not this is the optimal choice for stakeholders' requirements. We also conclude that our findings are largely driven by the choice of evaluation measure used by the forecast hub and that if this is misspecified then the forecast hub submissions may not be optimised to forecast users' expectations or requirements. Our work may be useful for forecast users to understand the inherent assumptions of the forecasts they are making use of and to researchers thinking about how to develop forecasts that perform similary to current multi-model and multi-team forecast ensembles that are trusted by stakeholders.

>>>>

We conclude that our simplified forecast model may have captured some of the dynamics of the hub ensemble but that more work needs to be done to understand the epidemiological model that represents its behaviour and whether or not this is the optimal choice for stakeholders' requirements. We also conclude that our findings are largely driven by the choice of evaluation measure used by the forecast hub and that if this is misspecified then the forecast hub submissions may not be optimised to forecast users' expectations or requirements. Our work may be useful for forecast users to understand the inherent assumptions of the forecasts they are making use of and to researchers thinking about how to develop forecasts that perform similarly to current multi-model and multi-team forecast ensembles that are trusted by stakeholders.
